Computing solution space properties of combinatorial optimization problems via generic tensor networks

### 2022-06-07 paper/suppl.tex
seperate suppl

%\documentclass[onefignum, onetabnum]{siamart190516}
\documentclass[a4paper, 12pt]{article}
%\usepackage{natbib}
%\usepackage[sort]{cite}
\pdfoutput=1
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{quoting}
\usepackage{upquote}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{cancel}
\usepackage[framemethod=TikZ]{mdframed}
\usetikzlibrary{shapes}
\usetikzlibrary{snakes}
\usetikzlibrary{shapes.geometric}
\usepackage{wrapfig}
%\usepackage{caption}
%\usepackage{algorithmic}
\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{rotating}
%\usepackage{cite}
\usepackage{booktabs}
%\usepackage{unicode-math}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
%\usepackage{algpseudocode}% http://ctan.org/pkg/algpseudocode
\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\makeatletter
\newsavebox{\@brx}
\newcommand{\llangle}[1][]{\savebox{\@brx}{\(\m@th{#1\langle}\)}%
  \mathopen{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
\newcommand{\rrangle}[1][]{\savebox{\@brx}{\(\m@th{#1\rangle}\)}%
  \mathclose{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
\makeatother
\usepackage{bbm}
\usepackage{jlcode}
\usepackage{graphicx}
\usepackage{amsmath,color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{indentfirst}
\usepackage{txfonts}
\setcounter{secnumdepth}{0}
%\usepackage[epsilon, tsrm, altpo]{backnaur}

\makeatletter
\def\parsept#1#2#3{%
    \def\nospace##1{\zap@space##1 \@empty}%
    \def\rawparsept(##1,##2){%
        \edef#1{\nospace{##1}}%
        \edef#2{\nospace{##2}}%
    }%
    \expandafter\rawparsept#3%
}
\makeatother
\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
\newcommand{\listingcaption}[1]%
{%
\refstepcounter{lstlisting}\hfill%
Listing \thelstlisting: #1\hfill%\hfill%
}%
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.7\hsize}X}
\usepackage{listings}
\lstset{
    language=Julia,
    basicstyle=\ttfamily\scriptsize,
    numberstyle=\scriptsize,
    % numbers=left,
    backgroundcolor=\color{gray!7},
    %backgroundcolor=\color{white},
    %frame=single,
    xleftmargin=2em,
    tabsize=2,
    rulecolor=\color{black!15},
    %title=\lstname,
    escapeinside={(*}{*)},
    breaklines=true,
    %breakatwhitespace=true,
    %framextopmargin=2pt,
    %framexbottommargin=2pt,
    frame=bt,
    extendedchars=true,
    inputencoding=utf8,
    columns=fullflexible,
    %escapeinside={(*@}{@*)},
}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=1000
\hbadness=1000

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

%Journal reference.  Comma sets off: name, vol, page, year
\def\journal #1, #2, #3, 1#4#5#6{{\sl #1~}{\bf #2}, #3 (1#4#5#6) }
\def\pr{\journal Phys. Rev., }
\def\prb{\journal Phys. Rev. B, }
\def\prl{\journal Phys. Rev. Lett., }
\def\pl{\journal Phys. Lett., }
%\def\np{\journal Nucl. Phys., }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[colorlinks, citecolor=blue]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\eqname}[1]{\stepcounter{equation}\tag{\theequation : #1}}
%%%%%% Shortcut related
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\out}{{\vx^L}}
\newcommand{\inp}{{\vx^0}}
\newcommand{\cquad}{{{ }_{\quad}}}
\newcommand{\pluseq}{\mathrel{+}=}
\newcommand{\minuseq}{\mathrel{-}=}
\newcommand{\vx}{{\mathbf{x}}}
\newcommand{\vg}{{\mathbf{g}}}
\newcommand{\vp}{{\mathbf{p}}}
\newcommand{\vy}{{\mathbf{y}}}
\newcommand{\Var}{{\mathrm{Var}}}
\newcommand{\Mean}{{\mathrm{E}}}
\newcommand{\vvalue}{{\texttt{value}}}
\newcommand{\grad}{{\texttt{grad}}}
\newcommand{\parameter}{{\texttt{parameter}}}
%%%%%% Convention related
\newcommand{\SWAP}{{\rm SWAP}}
\newcommand{\CNOT}{{\rm CNOT}}
\newcommand{\bigO}{{\mathcal{O}}}
\newcommand{\X}{{\rm X}}
\renewcommand{\H}{{\rm H}}
\newcommand{\Rx}{{\rm Rx}}
\renewcommand{\v}[1]{{\bf #1}}
\newcommand{\dataset}{{\mathcal{D}}}
\newcommand{\wfunc}{{\psi}}
\newcommand{\SU}{{\rm SU}}
\newcommand{\UU}{{\rm U}}
\newcommand{\thetav}{{\boldsymbol{\theta}}}
\newcommand{\gammav}{{\boldsymbol{\gamma}}}
\newcommand{\thetai}{{\theta^\alpha_l}}
\newcommand{\Expect}{{\mathbb{E}}}
\newcommand{\Tr}{{\rm Tr}}
\newcommand{\etc}{{\it etc~}}
\newcommand{\etal}{{\it etal~}}
\newcommand{\xset}{\mathbf{X}}
\newcommand{\fl}{\texttt{fl}}
\newcommand{\pdata}{\mathbf{\pi}}
\newcommand{\q}{\mathbf{q}}
\newcommand{\epdata}{\mathbf{\hat{\pi}}}
\newcommand{\gammaset}{\boldsymbol{\Gamma}}
\newcommand{\ei}{{\mathbf{e}_l^\alpha}}
\newcommand{\vtheta}{{\boldsymbol{\theta}}}
\newcommand{\sigmag}{{\nu}}
\newcommand{\sigmai}[2]{{\sigma^{#2}_{#1}}}
\newcommand{\qi}[1]{{q^{\alpha_{#1}}_{#1}}}
\newcommand{\BAS}{Bars-and-Stripes}
\newcommand{\circled}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
\newcommand{\qexpect}[1]{{\left\langle #1\right\rangle}}
\newcommand{\expect}[2]{{\mathop{\mathbb{E}}\limits_{\substack{#2}}\left[#1\right]}}
\newcommand{\var}[2]{{\mathop{\mathrm{Var}}\limits_{\substack{#2}}\left(#1\right)}}
\newcommand{\pshift}[1]{{p_{\thetav+#1}}}
\newcommand{\upcite}[1]{\textsuperscript{\cite{#1}}}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\Lst}[1]{Listing.~\ref{#1}}
\newcommand{\Tbl}[1]{Table~\ref{#1}}
\newcommand{\Sec}[1]{Sec.~\ref{#1}}
\newcommand{\App}[1]{Appendix~\ref{#1}}
\newcommand{\bra}[1]{\mbox{$\left\langle #1 \right|$}}
\newcommand{\ket}[1]{\mbox{$\left| #1 \right\rangle$}}
\newcommand{\braket}[2]{\mbox{$\left\langle #1 | #2 \right\rangle$}}
\newcommand{\tr}[1]{\mathrm{tr}\mbox{$\left[ #1\right]$}}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

%%%%%% Comment related
\newcommand{\red}[1]{[{\bf  \color{red}{ST: #1}}]}
\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{ST: #1}}}]}
\newcommand{\green}[1]{[{\bf  \color{green}{XG: #1}}]}
\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
\newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
\newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
\newcommand{\purple}[1]{[{\bf  \color{purple}{MC: #1}}]}
\newcommand{\xpurple}[1]{[{\bf  \color{purple}{\sout{MC: #1}}}]}
\newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}

\newcounter{example}
\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
   \noindent \textbf{Example~\theexample. #1} \rmfamily}{\medskip}

%\newtheorem{theorem}{\textit{Theorem}}
%\newtheorem{corollary}{\textit Branching Rule}
%\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
%\newtheorem{defin}[thm]{Definition}

\makeatother

%\externaldocument{ex_supplement}

\title{The supplementary material of ``Computing solution space properties of combinatorial optimization problems via generic tensor networks''
%\thanks{\funding{...}}
}

\author{
Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA.}
\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (contributed equally with Jin-Guo Liu to this work.).}
\and Madelyn Cain\footnotemark[2]
\and Mikhail D. Lukin\footnotemark[2]
\and Sheng-Tao Wang\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
}

\begin{document}

\maketitle

\tableofcontents

% REQUIRED
% 14N07  	Secant varieties, tensor rank, varieties of sums of powers

\section{Performance benchmarks}\label{sec:benchmark}
We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
The results are summarized in Figure~\ref{fig:benchmark}.
The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming~\cite{Courcelle1990, Fomin2013}.
To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
The main goal of this section is to show the relative computation time for calculating different solution space properties.

@@

Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
If we assume our contraction-order finding program has found the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
One can see that all the computation times in figure~\ref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
Among these benchmarks, computational tasks with data types real numbers, complex numbers, or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
These tasks usually compute much faster than ones with other element types in the same category.
Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
These data types do not include those defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr} or a data type containing them as a part.
In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.

We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.

@@

\section{Bounding the MIS enumeration space}\label{sec:bounding}
\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
    \caption{Bounded enumeration of maximum independent sets. Here, a circle is a tensor, an arrow specifies the execution direction of a function, $\overline A$ is the Boolean mask for $A$ and $\circ$ is the Hadamard (element-wise) multiplication. (a) is the forward pass with tropical algebra (\Eq{eq:tropical}) for computing $\alpha(G)$.
     (b) is the backward pass for computing Boolean gradient masks.
     (c) is the masked tensor network contraction with tropical algebra combined with sets (\Eq{eq:countingtropicalset}) for enumerating configurations.}
     \label{fig:bounding}
\end{figure}

When using the algebra in \Eq{eq:countingtropicalset} to enumerate all MISs, the program often stores significantly more intermediate configurations than necessary.
To reduce the space overhead, we will show how to bound the searching space using the MIS size $\alpha(G)$.
The bounded contraction consists of three stages as shown in \Fig{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
(b) Then, we compute a Boolean mask for each cached tensor, where we use a Boolean \texttt{true} to represent a tensor element having a contribution to the MIS and Boolean \texttt{false} otherwise.
(c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
The crucial part is computing the masks in step (b). Note that these masks correspond to tensor elements with non-zero gradients to the MIS size; we can compute these masks by back-propagating the gradients.
To derive the back-propagation rule for tropical tensor contraction,
we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
\begin{equation}
    A_{ij} \odot B_{jk} \leq C_{ik}.
\end{equation}
Here $\leq$ on tropical numbers are the same as the real-number algebra.
The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$,
but if doing this directly, one loses the advantage of using BLAS libraries~\cite{TropicalGEMM} for high performance.
Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 
\begin{equation}
    A_{ij} \leq C_{ik} \odot B_{jk}^{\circ -1}
\end{equation}
where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers).
The inequality still holds if we take the minimum over $k$: 
\begin{equation}
    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
\end{equation}
On the right-hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
\begin{equation}\label{eq:adrule}
\overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
\end{equation}
where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, Boolean false is treated as the tropical number $\mymathbb{0}$, and Boolean true is treated as the tropical number $\mymathbb{1}$.
This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.

@@

In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
Here, we show an alternative method with standard number types but with controllable round-off errors.
Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$. The linear equation thus becomes
\begin{equation}
\left(\begin{matrix}
1 & r & r^2 & \ldots & r^{\alpha(G)} \\
1 & r\omega & r^2\omega^2 & \ldots & r^{\alpha(G)} \omega^{\alpha(G)} \\
\vdots & \vdots & \vdots &\ddots & \vdots \\
1 & r\omega^{\alpha(G)} & r^2\omega^{2{\alpha(G)}} & \ldots & r^{\alpha(G)}\omega^{{\alpha(G)}^2}
\end{matrix}\right)
\left(\begin{matrix}
a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
\end{matrix}\right)
= \left(\begin{matrix}
y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
\end{matrix}\right).
\end{equation}

@@

\section{Computing maximum sum combination}\label{sec:maxsum}
Given two sets $A$ and $B$ of the same size $n$.
It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
The standard approach to solve the sum combination problem requires storing the variables in a heap --- a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
In the following, we show an algorithm with roughly the same complexity but does not need a heap.
This algorithm first sorts both $A$ and $B$ and then uses the bisection to find the $n$-th largest value in the sum combination.
The key point is we can count the number of entries greater than a specific value
in the sum combination of $A$ and $B$ in linear time.
As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
We summarize the algorithm as in Algorithm~\ref{alg:sumcombination}.

@@

\bibliographystyle{siamplain}
\bibliography{refs}

\end{document}

>>>>

\documentclass[review,supplement,onefignum,onetabnum]{siamart190516}
%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[linesnumbered, ruled, vlined, algo2e]{algorithm2e}
\input{shared}

\externaldocument{paper}

\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks}

% REQUIRED
% 14N07  	Secant varieties, tensor rank, varieties of sums of powers
\begin{document}
\maketitle

\section{Performance benchmarks}\label{sec:benchmark}
We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
The results are summarized in \Cref{fig:benchmark}.
The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming~\cite{Courcelle1990, Fomin2013}.
To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
The main goal of this section is to show the relative computation time for calculating different solution space properties.

@@

\Cref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
If we assume our contraction-order finding program has found the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
One can see that all the computation times in \Cref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
Among these benchmarks, computational tasks with data types real numbers, complex numbers, or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
These tasks usually compute much faster than ones with other element types in the same category.
Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
These data types do not include those defined in \Cref{eq:polynomial}, \Cref{eq:set}, \Cref{eq:ext-tropical} and \Cref{eq:expr} or a data type containing them as a part.
In \Cref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
but it may suffer from round-off errors (\Cref{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
In \Cref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \Cref{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.

We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Cref{fig:benchmark-maximal},
including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
\Cref{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
In \Cref{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.

@@

@@

In \Cref{sec:finitefield} in the main text, we show that the independence polynomial can be obtained by solving the linear equation \Cref{eq:lineareq} using the finite field algebra.
One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
Here, we show an alternative method with standard number types but with controllable round-off errors.
Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$. The linear equation thus becomes
\begin{equation}
\left(\begin{matrix}
1 & r & r^2 & \ldots & r^{\alpha(G)} \\
1 & r\omega & r^2\omega^2 & \ldots & r^{\alpha(G)} \omega^{\alpha(G)} \\
\vdots & \vdots & \vdots &\ddots & \vdots \\
1 & r\omega^{\alpha(G)} & r^2\omega^{2{\alpha(G)}} & \ldots & r^{\alpha(G)}\omega^{{\alpha(G)}^2}
\end{matrix}\right)
\left(\begin{matrix}
a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
\end{matrix}\right)
= \left(\begin{matrix}
y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
\end{matrix}\right).
\end{equation}

@@

\section{Computing maximum sum combination}\label{sec:maxsum}
Given two sets $A$ and $B$ of the same size $n$.
It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
The standard approach to solve the sum combination problem requires storing the variables in a heap --- a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
In the following, we show an algorithm with roughly the same complexity but does not need a heap.
This algorithm first sorts both $A$ and $B$ and then uses the bisection to find the $n$-th largest value in the sum combination.
The key point is we can count the number of entries greater than a specific value
in the sum combination of $A$ and $B$ in linear time.
As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
We summarize the algorithm as in \Cref{alg:sumcombination}.

@@

\bibliographystyle{siamplain}
\bibliography{refs}
\end{document}
